### 2017-01-20 R/ITHIM.Rmd
Fixed bug in ITHIM.Rmd

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

@@

ITHIMList <- as("ITHIMList", ITHIMList)
saveRDS(ITHIMList, file = "./data/ITHIMList.by.state.rds")

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("ggplot2")
library("devtools")
library("reshape2")
library("plyr")
library("dplyr")
```

@@

ITHIMList <- as(ITHIMList, "ITHIMList")
saveRDS(ITHIMList, file = "./data/ITHIMList.by.state.rds")
